### 2018-03-29 chapter6/ms.tex
Chapter 6 Stuff.

We consider two observing scenarios, survey and too

@@

\subsection{OpsSim Results}
\label{sec:ch6_opssim_results}
We have such and such LC and find this rate

Some number are detected twice

Try to fit them?

\subsection{ToO Results}
\label{sec:ch6_too_results}
From SNANA we have such and such results.

Try to fit LC returned by SNANA

Look at things like ability to measure ejecta properties as a function of time investment

\section{Discussion and Conclusion}
\label{sec:ch6_conc}
We have done some LSST stuff

>>>>

In this work, we consider the detectability and characterization of kilonovae in two unique observing situations. The first is the serendipitous detection of kilonovae in the LSST main survey independent of a GW trigger from LIGO. The second is triggered target-of-opportunity observations conducted by LSST in response to a GW trigger. We generate simulated observations for both scenarios as follows:

@@

\subsection{OpsSim Results}
\label{sec:ch6_opssim_results}
Detection and detection criteria. Including "rise" and "color"

General interpretation and models detected. Bright models are good. Faint models are bad.

Don't always get crucial rise or color information

BIG HISTOGRAM PLOT 1

Numbers of each value. Discuss plot.

Timing of detections and ability to detect early and late

BIG HISTOGRAM PLOT OF TIMES

Efficiencies

PLOT OF EFFICIENCIES?!

Expected rate and calculation

Implications

\subsection{ToO Results}
\label{sec:ch6_too_results}
Criteria same as used on LC from OpSim.

Same issue with models not being detected in standard 30s exposures.

eff plot

Discuss plot. Stress that this is relative to all models injected. Efficiency for the bright models is 100\%. 0\% for faint models.

Effect of Start Time

t_start plot

discuss plot. No effect on detection or ability to detect rise.

Effect of truncating time investment. None Really.

\section{Discussion and Conclusion}
\label{sec:ch6_conc}
We have done some LSST stuff. Major takeaway. LSST is good at ToO for bright KN. OpSim is okay at finding things over 10 years but unlikely to be associated with LIGO events.

Base exposures can only detect brightest novels. ToO needs to go deeper. Intermediate mass component possibly essential to GW170817 visibility.
